Environments and eval in R

### 2021-04-15 analysis/environments.Rmd
Fix environment classification

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    n_op = interp_eval,
    envir = envir_expression,
    envir_type,
    caller_expression,
    environment_class,
    enclos = enclos_expression
  ) -> E_envir

@@

```{r}
# 4 srcrefs will be counted twice, in package environments, and in caller environments
pack_envs <- env_classes %>% filter(is.na(new_env),  specific_env != "global")
nb_pack_sites <- n_distinct(pack_envs$src_ref)

nb_function_env_sites <- nb_caller_env_sites + nb_integer_sites

>>>>

  E_raw %>% select(
    run_package = package, #      The package which was run to trigger the eval
    ev_variant = eval_function, # Which eval variant was called
    duplicates = nb_ev_calls, #   Number of identical eval calls (weight)
    src_ref = eval_call_srcref, # Source ref for the eval call site
    file, #                       Script file name (name of this run)
    ev_package = eval_source, #   Package of the call site
    type = expr_resolved_type_tag, #   Argument type
    ev_call = eval_call_expression,
    ev_expr = expr_expression,
    n_op = interp_eval,
    hash = expr_resolved_hash,
    envir = envir_expression,
    envir_type,
    caller_expression,
    environment_class,
    enclos = enclos_expression
  ) -> E_envir

@@

```{r}
# in environment-class such as caller-n-packagename,
# package category wins
pack_envs <- env_classes %>% filter(is.na(new_env),  !specific_env %in% c("global", "empty"), !str_detect(specific_env, fixed("loop")))
nb_pack_sites <- n_distinct(pack_envs$src_ref)

# That might overestimate a bit...
nb_function_env_sites <- nb_caller_env_sites + nb_integer_sites
